---
title: "Assignment 9: Graduate School Admissions Analysis"
output: html_document
date: "2025-04-16"

---
These are the required packages
```{r}
library(tidyverse)
library(caret)
library(broom)
library(knitr)
library(pROC)
library(ggplot2)
library(modelr)
library(easystats)
library(GGally)
```

This is the data used
```{r load-data}

my_data <- read.csv("../../Data/GradSchool_Admissions.csv")

summary(my_data)
```

Here is a ggpairs plot
```{r ggpairs-plot, fig.width=10, fig.height=8}
library(GGally)

plot_multiple <- my_data %>%
  select(admit, gre, gpa, rank) %>%
  ggpairs()

plot_multiple
```

here are other plots comparing the topics to admit,

```{r admission-counts, fig.width=6, fig.height=4}
plot_adm <- ggplot(my_data, aes(x = factor(admit), fill = factor(admit))) +
  geom_bar() +
  labs(title = "Admission Counts")
plot_adm
```


```{r gre-by-admission, fig.width=6, fig.height=4}
plot_gpa <- ggplot(my_data, aes(x = gre, fill = factor(admit))) +
  geom_histogram(bins = 30, alpha = 0.7, position = 'identity') +
  labs(title = "GRE Scores by Admission")
plot_gpa
```

```{r gpa-by-admission, fig.width=6, fig.height=4}
ggplot(my_data, aes(x = gpa, fill = factor(admit))) +
  geom_histogram(bins = 30, alpha = 0.7, position = 'identity') +
  labs(title = "GPA by Admission")
```

```{r rank-by-admission, fig.width=6, fig.height=4}
ggplot(my_data, aes(x = rank, fill = factor(admit))) +
  geom_bar(position = "fill") +
  labs(title = "Admission Rate by Rank (Proportional)", y = "Proportion")
```

here is my model with summary

```{r model-full}
model_full <- glm(admit ~ gre + gpa + rank, data = my_data, family = "binomial")


summary(model_full)
```
This is the model in tidy format
```{r tidy-model-output}
library(broom)
tidy(model_full)
```



```{r}
set.seed(123)

train_index <- createDataPartition(my_data$admit, p = 0.8, list = FALSE)
train_data <- my_data[train_index, ]
test_data <- my_data[-train_index, ]
```
```{r}
model_train <- glm(admit ~ gre + gpa + rank, data = train_data, family = "binomial")

summary(model_train)
```

The predicted probabilitites on the test data, with the matrix.
```{r}
pred_probs <- predict(model_train, test_data, type = "response")

pred_class <- ifelse(pred_probs > 0.5, 1, 0)

conf_matrix <- confusionMatrix(factor(pred_class), factor(test_data$admit))
conf_matrix
```
The roc curve
```{r}


```{r roc-curve, fig.width=6, fig.height=4}

roc_curve <- pROC::roc(test_data$admit, pred_probs)


plot(roc_curve, main = "ROC Curve")


roc_auc <- pROC::auc(roc_curve)
roc_auc


```
A second model made being compared to the first one
```{r}

model_gre_gpa <- glm(admit ~ gre + gpa, data = train_data, family = "binomial")


AIC(model_train, model_gre_gpa)
```
